Paper 1: Vitis

### 2018-02-12 Paper-1-Vitis.Rmd
Commit from RStudio

```{r}
library(tidyverse)
library(skimr)
library(readxl)
read_excel("R_DiLP_all_species.xlsx")
excel_sheets("R_DiLP_all_species.xlsx")
read_excel("R_DiLP_Vitis_all_added.xlsx")
excel_sheets("R_DiLP_Vitis_all_added.xlsx")
```

@@

First, we applied a PCA to *Vitis acerifolia*.
```{r}
ac_ln <- read_excel("R_DiLP_Vitis_all_added.xlsx", sheet = "acerifolia.all.ln")
ac_ln_mat <- data.matrix(ac_ln, rownames.force = NA)
ac_ln_fixed <- ac_ln_mat[,-(1:3)]
ac_ln_fixed[ac_ln_fixed == 0] <- NA
pca_ac_all <- pca(ac_ln_fixed, method = "nipals", center = TRUE, nPcs = 5)
summary(pca_ac_all)
loadings(pca_ac_all)
scores_pca_ac <- scores(pca_ac_all)
scores_pca_ac_df <- as.data.frame(scores_pca_ac)
str(scores_pca_ac_df)
#ggplot(scores_pca_ac_df, aes(x = PC1, y = PC2, label = rownames(scores_pca_ac_df))) +
  #geom_col(x = PC1, y = PC2) +
  #ggtitle("PCA plot of Vitis acerifolia")
#attach row names
```

>>>>

```{r}
library(tidyverse)
library(tidyr)
library(skimr)
library(readxl)
read_excel("R_DiLP_all_species.xlsx")
excel_sheets("R_DiLP_all_species.xlsx")
read_excel("R_DiLP_Vitis_all_added.xlsx")
excel_sheets("R_DiLP_Vitis_all_added.xlsx")
```

@@

First, we applied a PCA to *Vitis acerifolia*.
```{r}
ac_ln <- read_excel("R_DiLP_Vitis_all_added.xlsx", sheet = "acerifolia.all.ln")
ac_ln_mat <- data.matrix(ac_ln, rownames.force = NA)
ac_ln_fixed <- ac_ln_mat[,-(1:3)]
ac_ln_fixed[ac_ln_fixed == 0] <- NA
#pca_ac_all <- pca(ac_ln_fixed, method = "nipals", center = TRUE, nPcs = 5)
bpca_ac_ll <- pca(ac_ln_fixed, method = "bpca", nPcs = 5)
summary(bpca_ac_ll)
loadings(bpca_ac_ll)
#summary(pca_ac_all)
#loadings(pca_ac_all)
print(bpca_ac_ll)
#print(pca_ac_all)
#slplot(pca_ac_all)
#loadings_pca_ac <- loadings(pca_ac_all)
#loadings_pca_ac_df <- as.data.frame(loadings_pca_ac)
#str(loadings_pca_ac_df)
#ggplot(loadings_pca_ac_df, aes(x = PC1, y = PC2, label = rownames(loadings_pca_ac_df))) +
  #geom_col(x = PC1, y = PC2) +
  #ggtitle("PCA plot of Vitis acerifolia")
#attach row names
```

We then applied a PCA to *Vitis aestivalis*.

```{r}
av_ln <- read_excel("R_DiLP_Vitis_all_added.xlsx", sheet = "aestivalis.all.ln")
av_ln_mat <- data.matrix(av_ln, rownames.force = NA)
av_ln_fixed <- av_ln_mat[,-(1:3)]
av_ln_fixed[av_ln_fixed == 0] <- NA
#pca_av_all <- pca(av_ln_fixed, method = "nipals", center = TRUE, nPcs = 5)
bpca_av_ll <- pca(av_ln_fixed, method = "bpca", nPcs = 5)
summary(bpca_av_ll)
loadings(bpca_av_ll)
#summary(pca_av_all)
#loadings(pca_av_all)
print(bpca_av_ll)
#print(pca_av_all)
#slplot(pca_av_all)
```

We then applied a PCA to *Vitis amurensis*.

```{r}
am_ln <- read_excel("R_DiLP_Vitis_all_added.xlsx", sheet = "amurensis.all.ln")
am_ln_mat <- data.matrix(am_ln, rownames.force = NA)
am_ln_fixed <- am_ln_mat[,-(1:3)]
am_ln_fixed[am_ln_fixed == 0] <- NA
#pca_am_all <- pca(am_ln_fixed, method = "nipals", center = TRUE, nPcs = 5)
bpca_am_ll <- pca(am_ln_fixed, method = "bpca", nPcs = 5)
summary(bpca_am_ll)
loadings(bpca_am_ll)
#summary(pca_am_all)
#loadings(pca_am_all)
print(bpca_am_ll)
#print(pca_am_all)
#slplot(pca_am_all)
```

Finally, we applied a PCA to *Vitis riparia*.

```{r}
r_ln <- read_excel("R_DiLP_Vitis_all_added.xlsx", sheet = "riparia.all.ln")
r_ln_mat <- data.matrix(r_ln, rownames.force = NA)
r_ln_fixed <- r_ln_mat[,-(1:3)]
r_ln_fixed[r_ln_fixed == 0] <- NA
#pca_r_all <- pca(r_ln_fixed, method = "nipals", center = TRUE, nPcs = 5)
bpca_r_ll <- pca(r_ln_fixed, method = "bpca", nPcs = 5)
summary(bpca_r_ll)
loadings(bpca_r_ll)
#summary(pca_r_all)
#loadings(pca_r_all)
print(bpca_r_ll)
#print(pca_r_all)
#slplot(pca_r_all)
beep(sound = 3, expr = NULL)
```

# Generalized Linear Modeling

First, we tested *Vitis acerifolia*.

```{r}
ac_glm <- glm(leaf~total.teeth, data = ac_all, family = gaussian())
summary(ac_glm)
plot(ac_glm)
```
